Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-17 appendix.qmd
Updated Figure 2

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = points_df, aes(x = x, y = y), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_segment(x = 0.175, y = 0.790, xend = -0.06, yend = 0.790, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.726, y = 0.790, xend = 0.50, yend = 0.790,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.313, y = 1.03, xend = 0.41, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.588, y = 1.03, xend = 0.48, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.313, y = 0.551, xend = 0.20, yend = 0.34,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.588, y = 0.551, xend = 0.67, yend = 0.34,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.451, y = 1.11, xend = 0.451, yend = 0.85,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.175, y = 0.949, xend = -0.02, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") #+
  # geom_segment(x = 0.161, y = 0.589, xend = 0.161, yend = 0.4, 
  #              arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  # geom_segment(x = 0.422, y = 0.438, xend = 0.25, yend = 0.3, 
  #              arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  # geom_segment(x = 0.683, y = 0.589, xend = 0.683, yend = 0.4, 
  #              arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  # geom_segment(x = 0.683, y = 0.890, xend = 0.5, yend = 0.82, 
  #              arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd")

>>>>

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = points_df, aes(x = x, y = y), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_segment(x = 0.175, y = 0.790, xend = -0.06, yend = 0.790, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.726, y = 0.790, xend = 0.50, yend = 0.790,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.313, y = 1.03, xend = 0.41, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.588, y = 1.03, xend = 0.48, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.313, y = 0.551, xend = 0.20, yend = 0.34,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.588, y = 0.551, xend = 0.67, yend = 0.34,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.451, y = 1.11, xend = 0.451, yend = 0.85,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.175, y = 0.949, xend = -0.02, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.175, y = 0.631, xend = 0.175, yend = 0.4,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.451, y = 0.472, xend = 0.25, yend = 0.3,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.726, y = 0.631, xend = 0.726, yend = 0.4,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd") +
  geom_segment(x = 0.726, y = 0.949, xend = 0.5, yend = 0.82,
               arrow = arrow(length = unit(0.02, "npc")), color = "#bdbdbd")
